--- 
title: "Modelos Lineales"
author:
  - "Sofía Villers Gómez"
  - "David Alberto Mateos Montes de Oca"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: alberto-mateos-mo/ModelosLinealesLibro
description: "Material para el curso Modelos Lineales de la Facultad de Ciencias, Universidad Nacional Autónoma de México"
---

# Modelos Lineales 2021-2{-}

```{r include = FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
library(tidyverse)
library(devtools)
```

Primera edición del libro de texto para el curso _Modelos Lineales_ de la Facultad de Ciencias.

## Detalles

Este libro fue escrito con [bookdown](http://bookdown.org/) usando [RStudio](http://www.rstudio.com/ide/).

Esta versión fue escrita con:

```{r message = FALSE, warning = FALSE, echo = FALSE}
all_pkgs <- renv::dependencies(path = "DESCRIPTION") %>% 
  pull(Package) 
session <- devtools::session_info(pkgs = all_pkgs)
session$platform
```

## Complementos

### Ejercicios Interactivos

Los ejercicios/ejemplos que acompañan este libro están disponibles a través de un paquete de R cuya instalación se hace de la siguiente manera:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("alberto-mateos-mo/ModelosLinealesFC")
```

Los ejercicios contenidos en el paquete están construidos con [learnr](https://rstudio.github.io/learnr/) y las indicaciones para abrirlos se dan al final de cada capítulo del libro.

El objetivo de los mismos es proveer al estudiante de los elementos prácticos necesarios para aplicar los diferentes modelos estudiados usando `R` y al mismo tiempo aprender a interpretar/usar los resultados obtenidos.

### Aplicación de análisis de datos

Hemos desarrollado una aplicación para realizar algunos análisis estadísticos a través de una interfaz gráfica que usaremos como recurso didáctico y que podrán usar para experimentar con algunos modelos sin la necesidad de escribir código.

La instalación de la app se hace con el siguiente comando:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("alberto-mateos-mo/data.analyseR")
```

Para lanzar la app debe usarse el siguiente comando:

```{r, eval=FALSE}
data.analyseR::run_app()
```


## Licencia {-}

This work is licensed under a [Creative Commons Attribution-ShareAlike 4.0 International License](https://creativecommons.org/licenses/by-sa/4.0/).

<center>
<i class="fab fa-creative-commons fa-2x"></i><i class="fab fa-creative-commons-by fa-2x"></i><i class="fab fa-creative-commons-sa fa-2x"></i>
</center>

*This is a human-readable summary of (and not a substitute for) the license.
Please see <https://creativecommons.org/licenses/by-sa/4.0/legalcode> for the full legal text.*

**You are free to:**

- **Share**---copy and redistribute the material in any medium or
  format

- **Remix**---remix, transform, and build upon the material for any
  purpose, even commercially.

The licensor cannot revoke these freedoms as long as you follow the
license terms.

**Under the following terms:**

- **Attribution**---You must give appropriate credit, provide a link
  to the license, and indicate if changes were made. You may do so in
  any reasonable manner, but not in any way that suggests the licensor
  endorses you or your use.
  
- **ShareAlike**---If you remix, transform, or build upon the material, you must distribute your contributions under the same license as the original. 

- **No additional restrictions**---You may not apply legal terms or
  technological measures that legally restrict others from doing
  anything the license permits.

**Notices:**

You do not have to comply with the license for elements of the
material in the public domain or where your use is permitted by an
applicable exception or limitation.

No warranties are given. The license may not give you all of the
permissions necessary for your intended use. For example, other rights
such as publicity, privacy, or moral rights may limit how you use the
material.

```{r include = FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```